\documentclass[../main.tex]{subfiles}

\begin{document}
	
	
	The first expected outcome of this research would be, a novel locomotion control strategy that could be adapted to the current reactive framework of the HyQ robot. This in place, is expected to improve robustness and flexibility thanks to its systematic design approach.
	
	On a larger scale, this research could provide, a strategy to systematically design and implement locomotion controllers to a variety of multi-legged robots. The proposed strategy, if proven to be effective for this project, could be easily adapted to several platforms that can design gaits via discrete event systems.  
	
	On the practical side, examples where max-plus algebra systems are used for locomotion are scarce. Furthermore, it was not found an example where this framework is implemented for robots with multiple joints in the legs. This would be a first experience using this strategy for this type of legs. This in place, would provide the analytical tools to reproduce this framework. In addition, software tools to implement discrete event systems in locomotion would be a natural consequence of the research process.
	
	It is clear, that if this strategy can manage to provide safe gait switching and parameter variation, robots would be able to overcome more difficult tasks while facing unstructured environments. In an ideal scenario, this strategy may represent a step towards successfully overcoming some of the greatest obstacles while encountering hazardous situations.  


\end{document}